A large-scale analysis of racial disparities in police stops across the

### 2019-06-07 lib/paper_results.Rmd
Progress

```{r setup, echo = FALSE}
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(here)
pfs <- readRDS(here::here("results", "prima_facie_stats.rds"))
# vod <- readRDS(here::here("results", "veil_of_darkness.rds"))
disp <- readRDS(here::here("results", "disparity.rds"))
mj <- readRDS(here::here("results", "marijuana_legalization_analysis.rds"))
```

@@

```{r stop_rates}
kable(pfs$stop_rates)
```
```{r search_rates}
kable(pfs$search_rates)
```

@@

```{r veil_of_darkness}
# TODO(danj/amyshoe):
```

\newpage
\begin{center}
\section{Disparity Analysis}
\end{center}
\begin{center}
\subsection{Outcome test results}
\end{center}
```{r disparity-city-hit_rates-table}
kable(disp$city$outcome$results$aggregate_hit_rates)
```
```{r disparity-state-hit_rates-table}
kable(disp$state$outcome$results$aggregate_hit_rates)
```
\newpage
```{r disparity-city-hit_rates-plot, fig.height = 3, fig.width = 7}
disp$city$outcome$plots$aggregate
```
```{r disparity-state-hit_rates-plot, fig.height = 3, fig.width = 7}
disp$state$outcome$plots$aggregate
```

>>>>

```{r setup, echo = FALSE}
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

pfs <- readRDS(here::here("results", "prima_facie_stats.rds"))
vod <- readRDS(here::here("results", "veil_of_darkness.rds"))
disp <- readRDS(here::here("results", "disparity.rds"))
mj <- readRDS(here::here("results", "marijuana_legalization_analysis.rds"))
```

\begin{center}
\section{Basic Numbers}
\end{center}

TODO

```{r basic_numbers}
# TODO(danj/amyshoe)
```

@@

```{r stop_rates}
pfs$stop_rates %>% 
  filter(subject_race %in% c("black", "white", "hispanic")) %>% 
  kable()
```

```{r search_rates}
pfs$search_rates %>% 
  filter(subject_race %in% c("black", "white", "hispanic")) %>% 
  kable()
```

@@

```{r veil_of_darkness-plot}
vod$states$plots$time_sliced$`Statewide, TX`
```

```{r veil_of_darkness-mod}
bind_rows(
  vod$dst$coefficients %>% 
    mutate(model = "DST: cities and counties"),  
  vod$cities$coefficients %>% 
    mutate(model = "Full year: cities"),
  vod$states$coefficients %>% 
    mutate(model = "Full year: states")
) %>% 
  select(model, is_dark, std_error, everything()) %>% 
  kable()

```
\newpage
\begin{center}
\section{Disparity Analysis}
\end{center}
\begin{center}
\subsection{Outcome test results}
\end{center}
```{r disparity-city-hit_rates-table}
kable(disp$city$outcome$results$aggregate_hit_rates)
```
```{r disparity-state-hit_rates-table}
kable(disp$state$outcome$results$aggregate_hit_rates)
```
\newpage
```{r disparity-city-hit_rates-plot, fig.height = 3, fig.width = 7}
disp$city$outcome$plots$aggregate
```
```{r disparity-state-hit_rates-plot, fig.height = 3, fig.width = 7}
disp$state$outcome$plots$aggregate
```
